Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-22 writing/DraftExposurePaper/DraftExposurePaper.Rmd
update count plots

```{r}
grid.arrange(b, c, ncol = 1)
```
Map of county exposures to the top 1000 county-storm pairs by wind-based exposure:

@@

```{r}
#Top 2000 storm-county pairs for wind events during tropical cyclones
wind_exposure <- county_events(counties = my_fips,
                              start_year = 1988, end_year = 2011,
                              event_type = "wind")
wind_2000 <- wind_exposure %>%
        slice(1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
wind_2000$value <- cut(wind_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_wind_2000 <- CountyChoropleth$new(wind_2000)
map_wind_2000$set_zoom(eastern_states)
map_wind_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_tornado_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Wind Events"
b <- map_wind_2000$render()
```

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
distance_count <- distance_exposure %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) 
distance_count$value <- cut(distance_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(7, name = "YlGnBu")

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
rain_count <- rain_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count))
rain_count$value <- cut(rain_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(7, name = "YlGnBu")

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
wind_count <- TS_wind_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count)) #Same size df as before (only 474 obs)
wind_count$value <- cut(wind_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(7, name = "YlGnBu")

@@

@@

```{r message = FALSE, warning = FALSE}
#Test
rain_exposure_2 <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 75, dist_limit = 100,
                             days_include = c(-1, 0, 1)) # Creates a data frame with 4040 obs (expected)
distance_rain_exposure <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 0, dist_limit = 100,
                             days_include = c(-1, 0, 1)) 
sum(distance_rain_exposure$tot_precip >= 75) # 4040 obs (meet both criteria)
sum(distance_rain_exposure$tot_precip < 75 & distance_rain_exposure$storm_dist <= 100) #7103 obs meet distance but 
                                                                                       #not rain criteria
```

>>>>

```{r}
grid.arrange(b, c, ncol = 1)
```

Map of county exposures to the top 1000 county-storm pairs by wind-based exposure:

@@

```{r}
#Top 2000 storm-county pairs for wind events during tropical cyclones
wind_exposure <- county_events(counties = my_fips,
                              start_year = 1988, end_year = 2011,
                              event_type = "wind")
wind_2000 <- wind_exposure %>%
        slice(1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
#Or
#wind_2000 <- wind_exposure %>%
        #group_by(fips) %>%
        #summarise(count = n()) %>%
        #arrange(desc(count))
        #slice(1:2000)
        #rename(region = fips) %>%
        #mutate(region = as.numeric(region), count = as.numeric(count))
wind_2000$value <- cut(wind_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_wind_2000 <- CountyChoropleth$new(wind_2000)
map_wind_2000$set_zoom(eastern_states)
map_wind_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_tornado_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Wind Events"
b <- map_wind_2000$render()
```

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
distance_count <- distance_exposure %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) 
distance_count$value <- cut(distance_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24, 26),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24", "25-26"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
rain_count <- rain_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count))
rain_count$value <- cut(rain_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24, 26),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24", "25-26"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
wind_count <- TS_wind_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count)) #Same size df as before (only 474 obs)
wind_count$value <- cut(wind_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24, 26),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24", "25-26"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

@@

```{r}
tornado_count <- tornado_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count))
tornado_count$value <- cut(tornado_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24, 26),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24", "25-26"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

map_tornado_count <- CountyChoropleth$new(tornado_count)
map_tornado_count$set_zoom(eastern_states)
map_tornado_count$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_tornado_count$title <- "Total Hits for Storm-County Pairs\nfor Tornado Events"
d <- map_tornado_count$render()
```

```{r}
wind_count <- wind_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count))
wind_count$value <- cut(wind_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24, 26),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24", "25-26"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

map_wind_count <- CountyChoropleth$new(wind_count)
map_wind_count$set_zoom(eastern_states)
map_wind_count$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_wind_count$title <- "Total Hits for Storm-County Pairs\nfor Wind Events"
e <- map_wind_count$render()
```

```{r}
flood_count <- flood_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count))
flood_count$value <- cut(flood_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24, 26),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24", "25-26"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

map_flood_count <- CountyChoropleth$new(flood_count)
map_flood_count$set_zoom(eastern_states)
map_flood_count$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_wind_count$title <- "Total Hits for Storm-County Pairs\nfor Flood Events"
f <- map_flood_count$render()
```

@@

```{r message = FALSE, warning = FALSE, echo = FALSE}
#Test
rain_exposure_2 <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 75, dist_limit = 100,
                             days_include = c(-1, 0, 1)) # Creates a data frame with 4040 obs (expected)
distance_rain_exposure <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 0, dist_limit = 100,
                             days_include = c(-1, 0, 1)) 
sum(distance_rain_exposure$tot_precip >= 75) # 4040 obs (meet both criteria)
sum(distance_rain_exposure$tot_precip < 75 & distance_rain_exposure$storm_dist <= 100) #7103 obs meet distance but 
                                                                                       #not rain criteria
```
